The Near and Mid-infrared photometric properties of known redshift $z\geq5$ Quasars

### 2020-01-16 tex/MNRAS_submission/rv1/referees_reply.txt

p. 1: You may want to end the first sentence of the right column of the Intro
with a statement that at z>5, relativistic time dilation also stretches the
photometric variability of the accretion disk as observed.

	    Now added.

p. 2, Fig. 1: Is it useful here to plot both filter sets if they are sufficiently
different? Please provide larger tick-marks for better readability in any case.

	   We have enlargened the  tick-marks.

	   The ZYJHK filters for UKIRT and VISTA *are* different, but
	   plotting both doesn't result in a clear figure. We have added an explicit link to:
	   d80b2t/VHzQ/SEDs/filters_vs_QSOstars_UKIRT.png and
	   d80b2t/VHzQ/SEDs/filters_vs_QSOstars_VISTA.png.

@@

p. 3, Fig. 2, caption or text: You should briefly comment on why the quasar
distribution has this gap in N(z) at z~5.5?. Is this because of the relativity
sensitivity across the filter curves, and/or the onset of complete GP-troughs at
z>5.7?

	Updated table 1,2 and figure 2. This gap has partly been filled in by recent (2018) 
	discoveries e.g. Yang et al. (2018) - which includes many of the 25 new objects that 
	we have recently added.

@@

p. 4, Fig. 3: Can you plot the small dots somewhat bigger for better visibility
without loss of information?

	We have updated the plot to make the dots bigger and to use the revised catalogue.

@@

    	Checked and updated.

p. 5: [My only (minor) scientific comment]: Re: ``although possible, we consider
it highly unlikely there would be more than one MIR source contributing to the
flux of a single UV/optically bright rest-frame quasar. Investigating this in
detail is very interesting but left to a future study. ''

I think it would be better to address now the number of expected contaminating
8--25 micron sources in the apertures used, as it can be done straightforwardly.
E.g., Driver et al. (2016, ApJ, 827, 107; astro-ph/1605.01523) --- the figures
you need for this estimate are actually best given as Fig. A4, A5 on the astro-ph
version. The redshift distribution of the sampled 8--25 micron foreground objects
is narrow enough and their K-corrections advantageous enough, that the objects
counts sharply turnover for AB(W3, W4) > 20--18 mag (left panels), and as a
consequence the normalized differential counts (right panels) --- especially in
W4 --- have most of their EBL energy emerging at AB~18--20 mag. As a consequence,
the relative number or probability of contaminating objects at AB>20 mag inside
your apertures should be rather small. A point worth mentioning, as it helps your
case.

		We have added approriate words in the text to address this good point.

@@

p. 6 Table 3: Should mention that the number of significant digits listed here
for the YJHK W1--W4 mags is not always warranted, but needed to verify the small
VIRCAM-WFCAM offsets in Table 5, This table is a very useful check of your global
photometric zeropoints.

We have updated both tables 3 and 5 with the new objects and some new VISTA photometry 
(increasing the end time to 20170101) and have added a line in the caption to Table 3.

### 2020-01-16 tex/MNRAS_submission/rv1/VHzQ_MNRAS_rv1.tex
Made last changes for now

\maketitle
\begin{abstract}
We assemble a catalogue of 488 spectroscopically confirmed very high
($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
and mid- (WISE W1234) infrared properties. 97\% of the VH$z$Q sample
is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of
coverage rather than lack of depth being the reason for the
non-detections. 362 (78\%) of the very high redshift quasars are
detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using
archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric
variability that might be expected from super-Eddington accretion. We
find 32 of the quasars have sufficient NIR measurements and
signal-to-noise to look for variability. Weak variability was detected
in multiple bands of SDSS J0959+0227, and very marginally in the
$Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, shows
significant differences between WFCAM and VISTA magnitudes in one band.
With supermassive black hole accretion likely to be redshift invariant
up to very high-redshift, further monitoring of these sources is
warranted.  All the data, analysis codes and plots used and generated
here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  %% trim=l b r t
  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
%  {../SEDs/filters_vs_QSOstars_z6pnt7.pdf}
  {figures/filters_vs_QSOstars_z6pnt7.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used in this paper. 
    The $ZYJHK$ filter curves are from UKIRT/WFCAM.  
    The $ZYJHK_{s}$ VISTA/VIRCAM filter curves are similar, but not identical to these. 
    The WISE passbands W1-4 are presented, though without the \citet{Brown2014b} W4 recalibration. 
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. }
  \label{fig:filters}
\end{figure}

@@

  The photometry in a single epoch image often has low
  signal-to-noise.  The advantage of matched aperture photometry on
  quasars is that co-adding is relatively simple if each epoch is taken
  in the same aperture and the aperture photometry has been corrected to
  total. Indeed, the standard aperture corrections work well for point
  sources. Coadding using the matched-aperture photometry can give
  better results for the photometry, where the individual epochs are
  taken from multiple projects with different field-centres and
  orientations and point-spread functions since the individual epoch
  scattered light, pixel distortion and aperture corrections can be
  applied with the correct weighting.

@@

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{AllWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \hline
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
  \label{tab:mir_detection}
\end{table}

@@

\begin{figure}
  %% trim=l b r t
  \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
  % {../detections/WISEmag_vs_coverage_20190605.pdf}
 {figures/WISEmag_vs_coverage_20190605.pdf}
  \centering
  \vspace{-14pt}
  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} Vega magnitude against signal-to-noise,
    colour coded by {\tt w$x$cov} the mean coverage depth, in each corresponding band.}
  \label{fig:WISEmag_vs_coverage}
\end{figure}
Before reporting on the detection rates, we investigate this effect
using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage} 
shows the WISE AllWISE magnitude versus signal-to-noise, colour coded
by {\tt w$x$cov} the mean coverage depth, in each corresponding
band. The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3
from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular
area with a radius of 8.25'' centered on the position of this
source. For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source
Catalog
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column
Descriptions} has further details). The {\tt w$x$cov} value takes into
account e.g., individual pixels in the measurement area that may be
masked or otherwise unusable (reducing the effective pixel count and
thus the mean coverage value) as well as pixels that are affected by
distortions across the across the focal plane in single-exposure
images (where this distortion is corrected when coadding to generate
the Atlas Images).

In the two shorter bands W1/2 we see the clear and expected
trend for brighter objects to have larger SNR, and also for the higher
signal to noise for objects with more exposures at a given
magnitude. The behaviour for the W3/4 bands is different, with two
populations clearly evident in W3 and although a bit more mixed, also
in W4. With the suggested split at SNR$>2$, and no obvious
R.A./Declination dependence seen, this behaviour is explained by the
fact that there are non-detections in W3/4 for objects (with high W1/2
SNR) that are reported in the AllWISE catalogue.

@@

The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with
(W1-W2) = -0.458 (i.e. 0.154 in Vega), and the WISE W1W2W3 color image
is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}. The reddest object in
(W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 0.719 (1.33 Vega).

@@

Using the extended datasets described in Section~\ref{sec:NIR_data},
we select objects with at least 8 measurements observed with intervals
of at least 30 days, in at least one filter. The the average
calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
with the signal-to-noise is required to be $\geq8$ (i.e. {\tt
aperJky3/aperJky3Err}$\geq$8). With these criteria, there are 18 WFCAM 
and 12 VISTA objects with 2 objects (SDSSJ0221-0342B $\&$ VIK J1148+0056) in
common to both, and this sample of 28 is our starting
point for variability investigations.

The clipped median and median absolute deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deviation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points. We apply the criteria 
$var>=3.$ to light-curves from the original measurements and also to light-curves 
where measurements have been averaged over different time-scales to improve 
the signal-to-noise. We found that two quasars showed signs of variability:
MMT J0215-0529 (see Fig.~\ref{fig:MMTJ0215-0529}) in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
SDSS J0959+0227 (see Fig.~\ref{fig:SDSSJ0959+0227}) in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
for $Y$ only. The $H$-band amplitude was 0.7 mag and the $Y$-band amplitude was
1.2 mag if averaged over 6 months, or 0.9 mag if averaged over 1 year.

@@

\begin{itemize}
  \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;
  \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$, though efforts are being made to address this
    \citep[e.g.,][]{YangJ2018a};
  \item 96.9\% of the VH$z$Q sample is detected in one or more NIR
    ($ZYJHK/K_{s}$) band;
  \item The 15 objects that are not detected in the NIR are due to
    lack of coverage rather than lack of depth;
  \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper
    unWISE W1 catalog.
  \item All of the $z\geq7$ quasars are detected in both unWISE W1 and
    W2.
  \item 28 of the quasars had enough NIR measurements and sufficient
    NIR measurements and signal-to-noise to look for variability. Weak
    variability was detected in multiple bands of SDSS J0959+0227, and
    very marginally in the Y-band of MMT J0215-0529. Only one quasar, SDSS
    J0349+0034 had significant differences between their WFCAM and VISTA
    magnitudes in one band, indicating variability.
 \end{itemize}

@@

\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
Object Name                      & R.A.               & Decl.  &  redshift  & difference \\
                                          & / deg             & / deg  &                & arcsec  \\
\hline
%% QSOs where pos changed (same name)
DELS J1048-0109               & +162.0795417 & -1.1611694        & 6.678   &     12.1 \\
SHELLQs J1429-0002          & +217.3342500 & -0.0353889        & 6.04    &  150.0 \\
DELS J1559+2212               & +239.7878750 & +22.2040083      & 6.07     &     3.0 \\
ATLAS J332.8017-32.1036 & +332.8017500 & -32.1035556      & 6.3394  &    3.2 \\
VIK J2318-3113                  & +349.5764625 & -31.2295417      & 6.4435  &  239.9 \\
\hline  \hline
\end{tabular}
\caption{Five quasars with updated coordinates.}
\label{tab:disagree_objs}
\end{table*}

>>>>

\maketitle
\begin{abstract}
We assemble a catalogue of 488 spectroscopically confirmed very high
($z\geq5.00$) redshift quasars and report their near- ($ZYJHK_{s}/K$)
and mid- (WISE W1234) infrared properties. 97\% of the VH$z$Q sample
is detected in one or more NIR ($ZYJHK/K_{s}$) band, with lack of
coverage rather than lack of depth being the reason for the
non-detections. 362 (78\%) of the very high redshift quasars are
detected at 3.4$\mu$m in the W1 band from the unWISE catalog and all
of the $z\geq7$ quasars are detected in both unWISE W1 and W2. Using
archival WFCAM/UKIRT and VIRCAM/VISTA data we check for photometric
variability that might be expected from super-Eddington accretion. We
find 32 of the quasars have sufficient NIR measurements and
signal-to-noise ratio to look for variability. Weak variability was detected
in multiple bands of SDSS J0959+0227, and very marginally in the
$Y$-band of MMT J0215-0529. Only one quasar, SDSS J0349+0034, shows
significant differences between WFCAM and VISTA magnitudes in one band.
With supermassive black hole accretion likely to be redshift invariant
up to very high-redshift, further monitoring of these sources is
warranted.  All the data, analysis codes and plots used and generated
here can be found at:
\href{https://github.com/d80b2t/VHzQ}{\tt github.com/d80b2t/VHzQ}.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  %% trim=l b r t
  % \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
%  {../SEDs/filters_vs_QSOstars_z6pnt7.pdf}
  {figures/filters_vs_QSOstars_z6pnt7.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used in this paper. 
    The $ZYJHK$ filter curves are from UKIRT/WFCAM.  
    The $ZYJHK_{s}$ VISTA/VIRCAM filter curves are similar, but not identical to these. 
    The main difference is the $K_s$ band in VISTA that is narrower than the
    WFCAM K, but there are other minor differences. The two sets of filters are
    shown in
    \href{https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters$\_$vs$\_$QSOstars$\_$UKIRT.png}{\tt
    github.com/d80b2t/VHzQ/SEDs/filters$\_$vs$\_$QSOstars$\_$UKIRT.png} and 
    \href{https://github.com/d80b2t/VHzQ/blob/master/SEDs/filters$\_$vs$\_$QSOstars$\_$VISTA.png}{\tt
    github.com/d80b2t/VHzQ/SEDs/filters$\_$vs$\_$QSOstars$\_$VISTA.png}
    respectively.
    The WISE passbands W1-4 are presented, though without the \citet{Brown2014b} W4 recalibration.
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. }
  \label{fig:filters}
\end{figure}

@@

  The photometry in a single epoch image often has a low
  signal-to-noise ratio. The advantage of matched aperture photometry on
  quasars is that co-adding is relatively simple if each epoch is taken
  in the same aperture and the aperture photometry has been corrected to
  total. Indeed, the standard aperture corrections work well for point
  sources. Coadding using the matched-aperture photometry can give
  better results for the photometry, where the individual epochs are
  taken from multiple projects with different field-centres and
  orientations and point-spread functions since the individual epoch
  scattered light, pixel distortion and aperture corrections can be
  applied with the correct weighting.

@@

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{AllWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \hline
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise ratio cut of {\tt w$x$snr}$>3.0$ has been used
    for each band.}
  \label{tab:mir_detection}
\end{table}

@@

\begin{figure}
  %% trim=l b r t
  \includegraphics[width=8.6cm, clip,trim=6mm 6mm 0mm 6mm]
  % {../detections/WISEmag_vs_coverage_20190605.pdf}
 {figures/WISEmag_vs_coverage_20190605.pdf}
  \centering
  \vspace{-14pt}
  \caption[]{WISE W1/2/3/4 {\tt w$x$mpro} Vega magnitude against signal-to-noise
  ratio, colour coded by {\tt w$x$cov} the mean coverage depth, in each
  corresponding band.}
  \label{fig:WISEmag_vs_coverage}
\end{figure}
Before reporting on the detection rates, we investigate this effect
using the AllWISE Source Catalog. Figure~\ref{fig:WISEmag_vs_coverage} 
shows the WISE AllWISE magnitude versus signal-to-noise ratio, colour coded
by {\tt w$x$cov} the mean coverage depth, in each corresponding
band. The {\tt w$123$cov} values are the mean pixel coverage in W1/2/3
from the W1/2/3 Atlas Tile Coverage Map within an aperture of circular
area with a radius of 8.25'' centered on the position of this
source. For {\tt w$4$cov} this radius is 16.5'' (the AllWISE Source
Catalog
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/expsup/sec2_1a.html#w2cov}{Column
Descriptions} has further details). The {\tt w$x$cov} value takes into
account e.g., individual pixels in the measurement area that may be
masked or otherwise unusable (reducing the effective pixel count and
thus the mean coverage value) as well as pixels that are affected by
distortions across the across the focal plane in single-exposure
images (where this distortion is corrected when coadding to generate
the Atlas Images).

In the two shorter bands W1/2 we see the clear and expected
trend for brighter objects to have larger SNR, and also for the higher
signal-to-noise ratio for objects with more exposures at a given
magnitude. The behaviour for the W3/4 bands is different, with two
populations clearly evident in W3 and although a bit more mixed, also
in W4. With the suggested split at SNR$>2$, and no obvious
R.A./Declination dependence seen, this behaviour is explained by the
fact that there are non-detections in W3/4 for objects (with high W1/2
SNR) that are reported in the AllWISE catalogue.

@@

The VH$z$Q with the bluest colour in (W1-W2) is DELS~J1048-0109, with
(W1-W2) = --0.458 (i.e. 0.154 in Vega), and the WISE W1W2W3 color image
is shown in Fig.~\ref{fig:VHzQ_W4s} {\it(a)}. The reddest object in
(W1-W2) is SHELLQs~J2223+0326 with (W1-W2) = 0.719 (1.33 Vega).

@@

Using the extended datasets described in Section~\ref{sec:NIR_data},
we select objects with at least 8 measurements observed with intervals
of at least 30 days, in at least one filter. The the average
calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
with the signal-to-noise ratio is required to be $\geq8$ (i.e. {\tt
aperJky3/aperJky3Err}$\geq$8). With these criteria, there are 18 WFCAM 
and 12 VISTA objects with 2 objects (SDSSJ0221-0342B $\&$ VIK J1148+0056) in
common to both, and this sample of 28 is our starting
point for variability investigations.

The clipped median and median absolute deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deviation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points. We apply the criteria 
$var>=3.$ to light-curves from the original measurements and also to light-curves 
where measurements have been averaged over different time-scales to improve 
the signal-to-noise ratio. We found that two quasars showed signs of
variability:
MMT J0215-0529 (see Fig.~\ref{fig:MMTJ0215-0529}) in the $Y$-band with an average time-scale of 30 days and amplitude of 0.3 mag, and 
SDSS J0959+0227 (see Fig.~\ref{fig:SDSSJ0959+0227}) in the $Y$ and $H$-bands, with timescales of 1 year or 6 months 
for $Y$ only. The $H$-band amplitude was 0.7 mag and the $Y$-band amplitude was
1.2 mag if averaged over 6 months, or 0.9 mag if averaged over 1 year.

@@

\begin{itemize}
  \item SDSS and Pan-STARRS1 together identified over half of the VH$z$Q sample;
  \item There remains a quasar ``redshift desert'' at $z\approx5.3-5.7$,  though
  efforts are being made to address this \citep[e.g.,][]{YangJ2018a};
  \item 96.9\% of the VH$z$Q sample is detected in one or more NIR
    ($ZYJHK/K_{s}$) band;
  \item The 15 objects that are not detected in the NIR are due to
    lack of coverage rather than lack of depth;
  \item 362 (78.2\%) VH$z$Qs are detected by WISE, e.g. in the deeper
    unWISE W1 catalog.
  \item All of the $z\geq7$ quasars are detected in both unWISE W1 and
    W2.
  \item 28 of the quasars had enough NIR measurements and sufficient
    NIR measurements and signal-to-noise ratio to look for variability. Weak
    variability was detected in multiple bands of SDSS J0959+0227, and
    very marginally in the Y-band of MMT J0215-0529. Only one quasar, SDSS
    J0349+0034 had significant differences between their WFCAM and VISTA
    magnitudes in one band, indicating variability.
 \end{itemize}

@@

\begin{table*}
\begin{tabular}{l r r r r r}
\hline  \hline
Object Name                      & R.A.               & Decl.  &  redshift  & difference \\
                                          & / deg             & / deg  &                & arcsec  \\
\hline
%% QSOs where pos changed (same name)
DELS J1048-0109               & +162.0795417 & --1.1611694        & 6.678   &   
12.1 \\
SHELLQs J1429-0002          & +217.3342500 & --0.0353889        & 6.04    & 
150.0 \\
DELS J1559+2212               & +239.7878750 & +22.2040083      & 6.07     &     3.0 \\
ATLAS J332.8017-32.1036 & +332.8017500 & --32.1035556      & 6.3394  &    3.2 \\
VIK J2318-3113                  & +349.5764625 & --31.2295417      & 6.4435  & 
239.9 \\
\hline  \hline
\end{tabular}
\caption{Five quasars with updated coordinates.}
\label{tab:disagree_objs}
\end{table*}
